---
title: "Capstone"
author: "Ammar Al-Hawashem"
date: "11/1/2021"
output: html_document
---
 
# File 2
# Description
This file includes mainly:
- Longitude of the venues
- Latitude of the venues
- Capacity of the venues
- Twitter followers for both the Home & Away Team
- Weekend feature
- The rank feature
- some revision
   
The resources for the rank (position) feature:
https://www.transfermarkt.com/saudi-professional-league/spieltagtabelle/wettbewerb/SA1/saison_id/2017/spieltag/2
https://web.archive.org/web/20160721071334/http:/www.slstat.com/spl2013-2014ar/alltable.php

#Load the required libraries
```{r}
#install.packages("broom")
#install.packages("stringr")
library(tidyverse)
library(rvest)
library(chron)
library(lubridate)
library(stringr)

```

#Import the dataset
```{r}
read.csv("SPL.csv") -> SPL
```

quick look into the dataset
```{r}
skimr::skim(SPL)
```
#Adjustment 
# Adj Teams
Since the data was collected from multiple resources, there is a great chance of mismatching in the names of teams and venues.
```{r}
unique(SPL$Home) 
```
remove the index to make them uniform
```{r}
str_replace_all(SPL$Home, "Al-Ittihad FC", "Al-Ittihad") -> SPL$Home
str_replace_all(SPL$Home, "Al Ahli SC", "Al Ahli") -> SPL$Home
str_replace_all(SPL$Home, "Al-Qadisiyahh", "Al-Qadisiyah") -> SPL$Home

#Then: replace the white space by "-"
str_replace_all(SPL$Home, " ", "-") -> SPL$Home

#The same steps with "Away"
str_replace_all(SPL$Away, "Al-Ittihad FC", "Al-Ittihad") -> SPL$Away
str_replace_all(SPL$Away, "Al Ahli SC", "Al Ahli") -> SPL$Away
str_replace_all(SPL$Away, "Al-Qadisiyahh", "Al-Qadisiyah") -> SPL$Away 

#Then: replace the white space by "-"
str_replace_all(SPL$Away, " ", "-") -> SPL$Away


```
# Adj Venues
Similarly, let's do if for the venues:
```{r}
unique(SPL$Venue) 
```
Adjust the irregularities from the multiple resources
```{r}
str_replace_all(SPL$Venue, "Prince Abdullah bin Jalawi Reserve Stadi...", "Prince Abdullah Bin Jalawi Sport City Stadium")  -> SPL$Venue
str_replace_all(SPL$Venue, "Prince Abdullah bin Jalawi Stadium", "Prince Abdullah Bin Jalawi Sport City Stadium")  -> SPL$Venue

str_replace_all(SPL$Venue, "AlAkhdoud Club Stadium", "Al-Ukhdood Stadium")  -> SPL$Venue

str_replace_all(SPL$Venue, "King Fahd International Stadium", "King Fahad International Stadium")  -> SPL$Venue

str_replace_all(SPL$Venue, "Prince Abdullah al-Faisal Stadium", "Prince Abdullah Al-Faisal Stadium")  -> SPL$Venue

str_replace_all(SPL$Venue, "King Abdul Aziz Stadium", "King Abdul Aziz Sport City Stadium")  -> SPL$Venue

str_replace_all(SPL$Venue, "Prince Faisal bin Fahad Stadium", "Prince Faysal Bin Fahad stadium")  -> SPL$Venue
str_replace_all(SPL$Venue, "Prince Faisal bin Fahd Stadium", "Prince Faysal Bin Fahad stadium")  -> SPL$Venue
str_replace_all(SPL$Venue, "Prince Faisal bin Fahd Fahd Training Pit...", "Prince Faysal Bin Fahad stadium")  -> SPL$Venue
str_replace_all(SPL$Venue, "Leadership Development Institute Stadium", "Prince Faysal Bin Fahad stadium")  -> SPL$Venue

str_replace_all(SPL$Venue, "Prince Saud bin Jalawi Stadium", "Prince Saud Bin Jalawi Sport City Stadium")  -> SPL$Venue
str_replace_all(SPL$Venue, "Ernst-Happel-Stadion", "Prince Saud Bin Jalawi Sport City Stadium")  -> SPL$Venue
str_replace_all(SPL$Venue, "Al-Qadasiya Club Stadium", "Prince Saud Bin Jalawi Sport City Stadium")  -> SPL$Venue
SPL$Venue[822] = "Prince Mohamed bin Fahd Stadium"

str_replace_all(SPL$Venue, "Al Majma'ah Sport City", "King Salman Bin Abdul Aziz Sport City Stadium")  -> SPL$Venue


str_replace_all(SPL$Venue, "Ar-Rass Stadium", "Al-Hazm Club Stadium")  -> SPL$Venue
str_replace_all(SPL$Venue, "Alhazm Club Stadium", "Al-Hazm Club Stadium")  -> SPL$Venue

str_replace_all(SPL$Venue, "Alansar Club Stadium", "Al-Ansar Club Stadium")  -> SPL$Venue

str_replace_all(SPL$Venue, "Al-Batin FC Stadium", "Al-Batin Club Stadium")  -> SPL$Venue
str_replace_all(SPL$Venue, "Department of Education Stadium", "Al-Batin Club Stadium")  -> SPL$Venue

str_replace_all(SPL$Venue, "King Abdullah Sports City", "King Abdullah International Stadium")  -> SPL$Venue
str_replace_all(SPL$Venue, "King Abdullah Sports City Reserve Stadiu...", "King Abdullah International Stadium")  -> SPL$Venue
str_replace_all(SPL$Venue, "King Abdullah International Stadium Reserve Stadiu...", "King Abdullah International Stadium")  -> SPL$Venue


str_replace_all(SPL$Venue, "Reserve Stadium in King Abdullah Sports ...", "King Abdullah International Reserve Stadium")  -> SPL$Venue

str_replace_all(SPL$Venue, "Prince Nayef bin Abdul Aziz Sports City ...", "Prince Mohamed bin Fahd Stadium")  -> SPL$Venue
SPL$Venue[953] = "Prince Saud Bin Jalawi Sport City Stadium"
SPL$Venue[986] = "Prince Saud Bin Jalawi Sport City Stadium"
SPL$Venue[871] = "Prince Saud Bin Jalawi Sport City Stadium"
SPL$Venue[844] = "Prince Mohamed bin Fahd Stadium"
SPL$Venue[769] = "Prince Mohamed bin Fahd Stadium"

str_replace_all(SPL$Venue, "Prince Abdullah Bin Jalawi Sport City Stadium\n", "Prince Abdullah Bin Jalawi Sport City Stadium")  -> SPL$Venue

SPL$Venue[731] = "King Abdullah International Stadium"

```
# King Abdullah Issue

```{r}
unique(SPL$Venue) 
```

There is a problem that there is two sport cities named after King Abudllah, and there are two teams at least play in each venue which made a huge confusion in the data

```{r}
SPL -> try

try %>%
  mutate(Venue = case_when(
    (Venue=="Prince Abdullah bin Abdul Aziz Stadium" & Home == "Al-Taawoun") ~ "King Abdullah Sport City Stadium",
     TRUE ~ as.character(Venue) )) -> try

try %>%
  mutate(Venue = case_when(
    (Venue=="Prince Abdullah bin Abdul Aziz Stadium" & Home == "Al-Raed") ~ "King Abdullah Sport City Stadium",
     TRUE ~ as.character(Venue) )) -> try

try %>%
  mutate(Venue = case_when(
    (Venue=="Prince Abdullah bin Abdul Aziz Stadium" & Home == "Al-Hazem") ~ "King Abdullah Sport City Stadium",
     TRUE ~ as.character(Venue) )) -> try

try %>%
  mutate(Venue = case_when(
    (Venue=="Prince Abdullah bin Abdul Aziz Stadium" & Home == "Al-Ahli") ~ "King Abdullah Sport City Stadium",
     TRUE ~ as.character(Venue) )) -> try

try %>%
  mutate(Venue = case_when(
    (Venue=="King Abdullah International Stadium" & Home == "Al-Taawoun") ~ "King Abdullah Sport City Stadium",
     TRUE ~ as.character(Venue) )) -> try

try %>%
  mutate(Venue = case_when(
    (Venue=="King Abdullah International Stadium" & Home == "Al-Raed") ~ "King Abdullah Sport City Stadium",
     TRUE ~ as.character(Venue) )) -> try


#Since everything is fine, we can return to our dataset (SPL) and remove this (try)
try -> SPL
remove(try)

# NOTE: game #700 played without attendance due to a regulation from the Disciplinary Committee
```
# Edit Week
Edit the column "week" which was "Weak" by mistake
```{r}
names(SPL)[names(SPL) == "Weak"] <- "Week"
```
# Add Long, Lat, Cap, followers
Let's now add the longitude, Latitude, & capacity for the 22 venues we have:

```{r}
SPL -> try
# Longitude
try %>% 
  mutate( Longitude = case_when(
  Venue ==  "Prince Abdullah Bin Jalawi Sport City Stadium" ~ 49.612778,
Venue =="Al-Ukhdood Stadium"~ 44.244720,
Venue =="King Fahad International Stadium"~ 46.839236,
Venue =="Prince Abdullah Al-Faisal Stadium"~ 39.251693,
Venue =="King Abdul Aziz Sport City Stadium"~ 39.974081,
Venue =="Prince Mohamed bin Fahd Stadium"~ 50.1141,
Venue =="Prince Faysal Bin Fahad stadium"~ 46.739745,
Venue =="King Abdullah Sport City Stadium"~ 43.9478,
Venue =="Prince Saud Bin Jalawi Sport City Stadium"~ 50.2052,
Venue =="King Salman Bin Abdul Aziz Sport City Stadium"~ 45.368019,
Venue =="Al-Hazm Club Stadium"~ 43.502350,
Venue =="Prince Mohammed bin Abdul Aziz Stadium"~ 42.490070,
Venue =="Al-Ansar Club Stadium"~ 39.545272,
Venue =="Al-Shoalah Club Stadium"~ 47.3473497,
Venue =="Al Orubah Club Stadium"~ 40.2110362,
Venue =="Prince Mohammed Alabdullah Stadium"~ 39.2188755,
Venue =="King Abdullah International Stadium"~ 39.164170,
Venue =="King Abdullah International Reserve Stadium"~ 39.164170,
Venue =="Al-Batin Club Stadium"~ 46.075254,
Venue =="King Saud University Stadium"~ 46.626176,
Venue =="Prince Khalid bin Sultan Stadium"~ 46.627541,
Venue =="Prince Sultan bin Abdul Aziz Stadium" ~ 42.597384
)  ) -> try

#Latitude
try %>% 
  mutate( Latitude = case_when(
  Venue ==  "Prince Abdullah Bin Jalawi Sport City Stadium" ~ 25.305833,
Venue =="Al-Ukhdood Stadium"~ 17.590280,
Venue =="King Fahad International Stadium"~ 24.788206,
Venue =="Prince Abdullah Al-Faisal Stadium"~21.446608,
Venue =="King Abdul Aziz Sport City Stadium"~ 21.485366,
Venue =="Prince Mohamed bin Fahd Stadium"~ 26.4272,
Venue =="Prince Faysal Bin Fahad stadium"~ 24.662599,
Venue =="King Abdullah Sport City Stadium"~ 26.3789,
Venue =="Prince Saud Bin Jalawi Sport City Stadium"~ 26.3699,
Venue =="King Salman Bin Abdul Aziz Sport City Stadium"~ 25.886929,
Venue =="Al-Hazm Club Stadium"~ 25.862347,
Venue =="Prince Mohammed bin Abdul Aziz Stadium"~ 18.223043,
Venue =="Al-Ansar Club Stadium"~ 24.514177,
Venue =="Al-Shoalah Club Stadium"~ 24.165976,
Venue =="Al Orubah Club Stadium"~ 30.005241,
Venue =="Prince Mohammed Alabdullah Stadium"~ 21.563392,
Venue =="King Abdullah International Stadium"~ 21.763220,
Venue =="King Abdullah International Reserve Stadium"~ 21.763220,
Venue =="Al-Batin Club Stadium"~ 28.448749,
Venue =="King Saud University Stadium"~ 24.730150,
Venue =="Prince Khalid bin Sultan Stadium"~ 24.804023,
Venue =="Prince Sultan bin Abdul Aziz Stadium" ~ 18.311279
)  ) -> try


#Capacity
try %>% 
  mutate( Capacity = case_when(
  Venue ==  "Prince Abdullah Bin Jalawi Sport City Stadium" ~ 27550,
Venue =="Al-Ukhdood Stadium"~ 2800,
Venue =="King Fahad International Stadium"~ 67000,
Venue =="Prince Abdullah Al-Faisal Stadium"~18000,
Venue =="King Abdul Aziz Sport City Stadium"~ 38000,
Venue =="Prince Mohamed bin Fahd Stadium"~ 26000,
Venue =="Prince Faysal Bin Fahad stadium"~ 22500,
Venue =="King Abdullah Sport City Stadium"~ 25000,
Venue =="Prince Saud Bin Jalawi Sport City Stadium"~ 21100,
Venue =="King Salman Bin Abdul Aziz Sport City Stadium"~ 7000,
Venue =="Al-Hazm Club Stadium"~ 3000,
Venue =="Prince Mohammed bin Abdul Aziz Stadium"~20000 ,
Venue =="Al-Ansar Club Stadium"~ 5000,
Venue =="Al-Shoalah Club Stadium"~ 6000,
Venue =="Al Orubah Club Stadium"~ 7000,
Venue =="Prince Mohammed Alabdullah Stadium"~21000 ,
Venue =="King Abdullah International Stadium"~ 60000,
Venue =="King Abdullah International Reserve Stadium"~ 500,
Venue =="Al-Batin Club Stadium"~ 6000,
Venue =="King Saud University Stadium"~ 25000,
Venue =="Prince Khalid bin Sultan Stadium"~ 10000,
Venue =="Prince Sultan bin Abdul Aziz Stadium" ~ 20000
)  ) -> try


#Twitter followers assuming it's constant during all the seasons
try %>% 
  mutate( H_Followers = case_when(
    Home == "Al-Fateh"  ~ 161.1*10^3,
    Home ==  "Najran"     ~ 31.2*10^3 ,
    Home == "Al-Shabab" ~ 414.9*10^3 ,
    Home ==   "Al-Ittihad" ~ 4*10^6,
  Home =="Al-Hilal" ~ 9.6*10^6 ,
  Home ==    "Al-Wehda" ~ 226.6*10^3 ,
  Home ==  "Al-Ahli"   ~2*10^6 ,
 Home == "Al-Ettifaq" ~ 226.5*10^3,
  Home ==  "Al-Nassr"  ~ 3.1*10^6,
  Home =="Al-Taawon" ~ 208.7*10^3,
  Home =="Al-Qadisiya" ~ 91.7*10^3,
   Home =="Al-Faisaly" ~ 103.9*10^3,
  Home == "Al-Raed" ~149.2*10^3 ,
  Home =="Al-Hazem"  ~ 49.7*10^3,
  Home =="Hajer"    ~ 21.9*10^3,
   Home =="Al-Ansar" ~ 17.3*10^3,
  Home ==  "Al-Shoalah" ~20.6*10^3 ,
  Home == "Al-Nahda"   ~ 13.1*10^3,
  Home =="Al-Orubah"   ~ 28*10^3 ,
   Home =="Al-Shoulla"~ 20.6*10^3,
  Home ==  "Al-Orobah" ~28*10^3 ,
  Home == "Al-Khaleej" ~ 78.1*10^3,
  Home =="Al-Taawoun" ~ 208.7*10^3,
   Home =="Al-Qadsiah"~ 91.7*10^3,
  Home == "Al-Batin" ~ 98.2*10^3,
  Home =="Al-Fayha" ~ 70.8*10^3 ,
 Home == "Ohod" ~79.7*10^3 ,
 Home == "Al-Adalah" ~ 25.4*10^3,
 Home == "Damac" ~ 72.4*10^3,
 Home ==  "Abha" ~ 56.8*10^3
  )) ->try
#Simillarly for  Away teams
try %>% 
  mutate( A_Followers = case_when(
    Away == "Al-Fateh" ~ 161.1*10^3,
    Away ==  "Najran"     ~ 31.2*10^3 ,
    Away == "Al-Shabab" ~ 414.9*10^3 ,
    Away ==   "Al-Ittihad" ~ 4*10^6,
  Away =="Al-Hilal" ~ 9.6*10^6 ,
  Away ==    "Al-Wehda" ~ 226.6*10^3 ,
  Away ==  "Al-Ahli"   ~2*10^6 ,
 Away == "Al-Ettifaq" ~ 226.5*10^3,
  Away ==  "Al-Nassr"  ~ 3.1*10^6,
  Away =="Al-Taawon" ~ 208.7*10^3,
  Away =="Al-Qadisiya" ~ 91.7*10^3,
   Away =="Al-Faisaly" ~ 103.9*10^3,
  Away == "Al-Raed" ~149.2*10^3 ,
  Away =="Al-Hazem"  ~ 49.7*10^3,
  Away =="Hajer"    ~ 21.9*10^3,
   Away =="Al-Ansar" ~ 17.3*10^3,
  Away ==  "Al-Shoalah" ~20.6*10^3 ,
  Away == "Al-Nahda"   ~ 13.1*10^3,
  Away =="Al-Orubah"   ~ 28*10^3 ,
   Away =="Al-Shoulla"~ 20.6*10^3,
  Away ==  "Al-Orobah" ~28*10^3 ,
  Away == "Al-Khaleej" ~ 78.1*10^3,
  Away =="Al-Taawoun" ~ 208.7*10^3,
   Away =="Al-Qadsiah"~ 91.7*10^3,
  Away == "Al-Batin" ~ 98.2*10^3,
  Away =="Al-Fayha" ~ 70.8*10^3 ,
 Away == "Ohod" ~79.7*10^3 ,
 Away == "Al-Adalah" ~ 25.4*10^3,
 Away == "Damac" ~ 72.4*10^3,
 Away ==  "Abha" ~ 56.8*10^3
  )) ->try
```
#adj teams #2
```{r}
#You may notice that even after revision, there are four teams has two names, so let's uniform them:
str_replace_all(try$Home, "Al-Shoalah", "Al-Shoulla") -> try$Home
str_replace_all(try$Home, "Al-Shoulla", "Al-Shoulla") -> try$Home
str_replace_all(try$Home, "Al-Orubah", "Al-Orobah") -> try$Home
str_replace_all(try$Home, "Al-Taawon", "Al-Taawoun") -> try$Home
str_replace_all(try$Home, "Al-Qadisiya", "Al-Qadisiyah") -> try$Home
str_replace_all(try$Home, "Al-Qadsiah", "Al-Qadisiyah") -> try$Home
#AWay
str_replace_all(try$Away, "Al-Shoalah", "Al-Shoulla") -> try$Away
str_replace_all(try$Away, "Al-Shoulla", "Al-Shoulla") -> try$Away
str_replace_all(try$Away, "Al-Orubah", "Al-Orobah") -> try$Away
str_replace_all(try$Away, "Al-Taawon", "Al-Taawoun") -> try$Away
str_replace_all(try$Away, "Al-Qadisiya", "Al-Qadisiyah") -> try$Away
str_replace_all(try$Away, "Al-Qadsiah", "Al-Qadisiyah") -> try$Away
```


Check 
```{r}
skimr::skim(
try  
)
#let's return our SPL and delete the try version
try -> SPL
remove(try)
```

#Add families feature
The women has been allowed to be present since 2018-01-12 
```{r}
SPL -> try

try %>% 
  mutate(Families = case_when(
    Date >="2018-01-12" ~ "Yes",
    TRUE ~ "No"
  )) -> try
```
# Add period feature
Let's divide the matches according to the time: to daytime & night 
```{r}
try %>% 
  mutate(Period = case_when(
    Time >="17:00:00" ~ "Night",
    TRUE ~ "Daytime"
  )) -> try
```

Let's divide the matches further according is it weekend (including Thursday's) or weekday. In addition, I'll consider the public holidays in Saudi Arabia as weekends (Eid Al-Adha & Saudi National Day).

# Add Weekend feature
which includes holidays
```{r}
# The dates for the holidays
try %>% 
  mutate(Weekend = case_when(
    Day =="Saturday" |
      Day =="Thursday" |
      Day =="Friday" |
      (Date >= "2010-11-12" & Date <= "2010-11-22") |
      (Date >= "2011-11-02" & Date <= "2011-11-12") |
      (Date >= "2012-10-21" & Date <= "2012-10-31") |
      (Date >= "2013-10-10" & Date <= "2013-10-20") |
      (Date >= "2014-09-26" & Date <= "2014-10-08") |
      (Date >= "2015-09-24" & Date <= "2015-10-02") |
      (Date >= "2016-09-10" & Date <= "2016-09-15") |
      (Date >= "2017-09-02" & Date <= "2017-09-05") |
      (Date >= "2018-08-20" & Date <= "2018-08-23") |
      (Date >= "2019-08-10" & Date <= "2019-08-13") |
      Date == "2010-09-23" |
      Date == "2011-09-23" |
      Date == "2012-09-23" |
      Date == "2013-09-23" |
      Date == "2014-09-23" |
      Date == "2015-09-23" |
      Date == "2016-09-23" |
      Date == "2017-09-23" |
      Date == "2018-09-23" |
      Date == "2019-09-23" 
      ~ "Yes",
    TRUE ~ "No"
  )) -> try
```

```{r}
try -> SPL
remove(try)
```

```{r}
#Adjustment
str_replace_all(SPL$Home, "Al-Qadisiyahh", "Al-Qadisiyah") -> SPL$Home
str_replace_all(SPL$Away, "Al-Qadisiyahh", "Al-Qadisiyah") -> SPL$Away

SPL %>% 
  mutate(Index = c(1:1861)) -> SPL
SPL <- SPL[,c(19,1:18)]

# workflow has been saved (CapstoneV1)

```
#Add position Feature
Let's add position Home & Position Away which represent the standing of each team before the fixture
```{r}
SPL %>% 
add_column(PosH = 0,PosA = 0) -> SPL
```
# Split the seasons
Let's Separate the seasons to fill the standing
Note: we cannot use loop since some seasons have more teams
```{r}
s10 <- SPL[1:182,]
s11 <- SPL[183:364,]
s12  <- SPL[365:546,]
s13  <- SPL[547:728,]
s14  <- SPL[729:910,]
s15  <- SPL[911:1092,]
s16  <- SPL[1093:1274,]
s17  <- SPL[1275:1456,]
s18  <- SPL[1457:1696,]
s19  <- SPL[1697:1861,]
```

The resources for the position/per round:

https://www.transfermarkt.com/saudi-professional-league/spieltagtabelle/wettbewerb/SA1/saison_id/2017/spieltag/2
https://web.archive.org/web/20160721071334/http:/www.slstat.com/spl2013-2014ar/alltable.php

```{r}
#Season2010
Qadisiyah<- c(1,1,5,5,4,6,6,7,7,10,10,11,9,10,12,12,10,11,10,11,12,12,13,12,12,13)
Raed<- c(1,2,2,3,3,3,5,5,6,6,8,8,7,7,7,7,7,8,8,8,7,8,10,10,10,9)
Ittihad<- c(1,3,3,2,2,2,1,1,1,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2)
Ahli<- c(1,4,8,8,10,11,12,13,11,12,12,12,12,12,9,8,8,7,7,7,8,7,7,8,8,7)
Hilal<- c(1,5,4,1,1,1,2,2,2,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1)
Nassr<- c(1,6,1,4,5,4,3,4,4,3,4,3,3,4,3,3,3,4,3,4,3,3,3,3,5,4)
Faisaly<- c(1,7,10,13,13,13,10,11,9,7,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6)
Wehda<- c(1,8,9,11,12,10,13,9,8,9,7,7,8,8,8,9,9,10,9,9,11,11,11,11,11,12)
Ettifaq<- c(1,9,7,7,6,5,4,3,5,4,3,5,4,3,4,5,4,5,5,3,4,5,5,4,3,3)
Hazem<- c(1,10,12,12,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14)
Taawoun<- c(1,11,6,6,7,7,8,8,10,8,9,9,10,9,11,11,12,12,12,10,9,9,8,7,7,8)
Najran<- c(1,12,11,14,11,12,9,10,12,11,11,10,11,11,13,13,13,13,13,13,13,13,12,13,13,11)
Fateh<- c(1,13,13,9,8,9,11,12,13,13,13,13,13,13,10,10,11,9,11,12,10,10,9,9,9,10)
Shabab<- c(1,14,14,10,9,8,7,6,3,5,5,4,5,5,5,4,5,3,4,5,5,4,4,5,4,5)

#The difficulties with the loop:
  # 1- There are some postponed matches which made relying in the round (week) is not feasbile
  # 2- Not all the seaosns have the same number of matches
  # 3- The two teams (Home & Away are in the same row)

# The logic of the loop:
  #   i is the the number of the game (row)
  #   j is the index of the rank 
  # One loop for each team/season

##1
i=1
j=1
while (i<=182){
  if(s10$Home[i] == "Najran") {
    s10$PosH[i] <- Najran[j]
    j=j+1 }
    else if (s10$Away[i] == "Najran") {
      s10$PosA[i] <- Najran[j]
      j=j+1}
  i=i+1}
  
##2
i=1
j=1
while (i<=182){
  if(s10$Home[i] == "Al-Qadisiyah") {
    s10$PosH[i] <- Qadisiyah[j]
    j=j+1 }
    else if (s10$Away[i] == "Al-Qadisiyah") {
      s10$PosA[i] <- Qadisiyah[j]
      j=j+1}
  i=i+1}
##3
i=1
j=1
while (i<=182){
  if(s10$Home[i] == "Al-Raed") {
    s10$PosH[i] <- Raed[j]
    j=j+1 }
    else if (s10$Away[i] == "Al-Raed") {
      s10$PosA[i] <- Raed[j]
      j=j+1}
  i=i+1}
##4
i=1
j=1
while (i<=182){
  if(s10$Home[i] == "Al-Ittihad") {
    s10$PosH[i] <- Ittihad[j]
    j=j+1 }
    else if (s10$Away[i] == "Al-Ittihad") {
      s10$PosA[i] <- Ittihad[j]
      j=j+1}
  i=i+1}

##5
i=1
j=1
while (i<=182){
  if(s10$Home[i] == "Al-Ahli") {
    s10$PosH[i] <- Ahli[j]
    j=j+1 }
    else if (s10$Away[i] == "Al-Ahli") {
      s10$PosA[i] <- Ahli[j]
      j=j+1}
  i=i+1}

##6
i=1
j=1
while (i<=182){
  if(s10$Home[i] == "Al-Hilal") {
    s10$PosH[i] <- Hilal[j]
    j=j+1 }
    else if (s10$Away[i] == "Al-Hilal") {
      s10$PosA[i] <- Hilal[j]
      j=j+1}
  i=i+1}

##7
i=1
j=1
while (i<=182){
  if(s10$Home[i] == "Al-Nassr") {
    s10$PosH[i] <- Nassr[j]
    j=j+1 }
    else if (s10$Away[i] == "Al-Nassr") {
      s10$PosA[i] <- Nassr[j]
      j=j+1}
  i=i+1}


##8
i=1
j=1
while (i<=182){
  if(s10$Home[i] == "Al-Taawoun") {
    s10$PosH[i] <- Taawoun[j]
    j=j+1 }
    else if (s10$Away[i] == "Al-Taawoun") {
      s10$PosA[i] <- Taawoun[j]
      j=j+1}
  i=i+1}

##9
i=1
j=1
while (i<=182){
  if(s10$Home[i] == "Al-Faisaly") {
    s10$PosH[i] <- Faisaly[j]
    j=j+1 }
    else if (s10$Away[i] == "Al-Faisaly") {
      s10$PosA[i] <- Faisaly[j]
      j=j+1}
  i=i+1}

##10
i=1
j=1
while (i<=182){
  if(s10$Home[i] == "Al-Hazem") {
    s10$PosH[i] <- Hazem[j]
    j=j+1 }
    else if (s10$Away[i] == "Al-Hazem") {
      s10$PosA[i] <- Hazem[j]
      j=j+1}
  i=i+1}

##11
i=1
j=1
while (i<=182){
  if(s10$Home[i] == "Al-Wehda") {
    s10$PosH[i] <- Wehda[j]
    j=j+1 }
    else if (s10$Away[i] == "Al-Wehda") {
      s10$PosA[i] <- Wehda[j]
      j=j+1}
  i=i+1}


##12
i=1
j=1
while (i<=182){
  if(s10$Home[i] == "Al-Ettifaq") {
    s10$PosH[i] <- Ettifaq[j]
    j=j+1 }
    else if (s10$Away[i] == "Al-Ettifaq") {
      s10$PosA[i] <- Ettifaq[j]
      j=j+1}
  i=i+1}

##13
i=1
j=1
while (i<=182){
  if(s10$Home[i] == "Al-Fateh") {
    s10$PosH[i] <- Fateh[j]
    j=j+1 }
    else if (s10$Away[i] == "Al-Fateh") {
      s10$PosA[i] <- Fateh[j]
      j=j+1}
  i=i+1}
##14
i=1
j=1
while (i<=182){
  if(s10$Home[i] == "Al-Shabab") {
    s10$PosH[i] <- Shabab[j]
    j=j+1 }
    else if (s10$Away[i] == "Al-Shabab") {
      s10$PosA[i] <- Shabab[j]
      j=j+1}
  i=i+1}

# #Season2011
Ittihad<- c(1,1,6,9,6,7,6,6,5,5,5,6,5,5,5,6,6,6,6,6,7,6,6,6,6,6)
Shabab<- c(1,2,1,2,1,2,1,1,1,2,1,1,1,1,2,3,2,2,2,1,1,1,1,1,1,1)
Hilal<- c(1,3,9,4,3,3,3,3,3,3,2,2,2,2,1,1,3,4,3,3,3,3,3,3,3,3)
Ahli<- c(1,4,3,1,4,4,4,4,4,4,4,3,3,3,3,2,1,1,1,2,2,2,2,2,2,2)
Ettifaq<- c(1,5,2,3,2,1,2,2,2,1,3,4,4,4,4,4,4,3,4,4,4,4,4,4,4,4)
Nassr<- c(1,6,10,7,11,8,8,5,7,6,7,5,6,7,7,7,7,7,7,7,6,7,7,7,7,7)
Fateh<- c(1,7,4,5,5,5,5,7,6,7,6,7,7,6,6,5,5,5,5,5,5,5,5,5,5,5)
Najran<- c(1,8,11,13,12,10,12,12,9,9,9,9,10,8,8,8,10,11,9,10,8,8,8,8,8,9)
Hajer<- c(1,9,12,10,9,12,11,9,11,11,12,12,8,11,13,11,8,9,10,9,10,10,11,11,11,11)
Ansar<- c(1,10,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14)
Qadisiyah<- c(1,11,5,8,8,6,7,8,10,10,10,10,11,9,9,9,11,10,11,11,12,12,13,13,13,13)
Raed<- c(1,12,13,12,13,13,13,13,13,13,13,11,12,10,11,12,13,13,13,12,11,11,9,10,9,10)
Taawoun<- c(1,13,8,11,10,11,9,10,12,12,11,13,13,13,12,13,12,12,12,13,13,13,12,12,12,12)
Faisaly<- c(1,14,7,6,7,9,10,11,8,8,8,8,9,12,10,10,9,8,8,8,9,9,10,9,10,8)


##1
i=1
j=1
while (i<=182){
  if(s11$Home[i] == "Najran") {
    s11$PosH[i] <- Najran[j]
    j=j+1 }
    else if (s11$Away[i] == "Najran") {
      s11$PosA[i] <- Najran[j]
      j=j+1}
  i=i+1}

##2
i=1
j=1
while (i<=182){
  if(s11$Home[i] == "Al-Qadisiyah") {
    s11$PosH[i] <- Qadisiyah[j]
    j=j+1 }
    else if (s11$Away[i] == "Al-Qadisiyah") {
      s11$PosA[i] <- Qadisiyah[j]
      j=j+1}
  i=i+1}
##3
i=1
j=1
while (i<=182){
  if(s11$Home[i] == "Al-Raed") {
    s11$PosH[i] <- Raed[j]
    j=j+1 }
    else if (s11$Away[i] == "Al-Raed") {
      s11$PosA[i] <- Raed[j]
      j=j+1}
  i=i+1}
##4
i=1
j=1
while (i<=182){
  if(s11$Home[i] == "Al-Ittihad") {
    s11$PosH[i] <- Ittihad[j]
    j=j+1 }
    else if (s11$Away[i] == "Al-Ittihad") {
      s11$PosA[i] <- Ittihad[j]
      j=j+1}
  i=i+1}

##5
i=1
j=1
while (i<=182){
  if(s11$Home[i] == "Al-Ahli") {
    s11$PosH[i] <- Ahli[j]
    j=j+1 }
    else if (s11$Away[i] == "Al-Ahli") {
      s11$PosA[i] <- Ahli[j]
      j=j+1}
  i=i+1}

##6
i=1
j=1
while (i<=182){
  if(s11$Home[i] == "Al-Hilal") {
    s11$PosH[i] <- Hilal[j]
    j=j+1 }
    else if (s11$Away[i] == "Al-Hilal") {
      s11$PosA[i] <- Hilal[j]
      j=j+1}
  i=i+1}

##7
i=1
j=1
while (i<=182){
  if(s11$Home[i] == "Al-Nassr") {
    s11$PosH[i] <- Nassr[j]
    j=j+1 }
    else if (s11$Away[i] == "Al-Nassr") {
      s11$PosA[i] <- Nassr[j]
      j=j+1}
  i=i+1}


##8
i=1
j=1
while (i<=182){
  if(s11$Home[i] == "Al-Taawoun") {
    s11$PosH[i] <- Taawoun[j]
    j=j+1 }
    else if (s11$Away[i] == "Al-Taawoun") {
      s11$PosA[i] <- Taawoun[j]
      j=j+1}
  i=i+1}

##9
i=1
j=1
while (i<=182){
  if(s11$Home[i] == "Al-Faisaly") {
    s11$PosH[i] <- Faisaly[j]
    j=j+1 }
    else if (s11$Away[i] == "Al-Faisaly") {
      s11$PosA[i] <- Faisaly[j]
      j=j+1}
  i=i+1}

##10
i=1
j=1
while (i<=182){
  if(s11$Home[i] == "Hajer") {
    s11$PosH[i] <- Hajer[j]
    j=j+1 }
    else if (s11$Away[i] == "Hajer") {
      s11$PosA[i] <- Hajer[j]
      j=j+1}
  i=i+1}

##11
i=1
j=1
while (i<=182){
  if(s11$Home[i] == "Al-Ansar") {
    s11$PosH[i] <- Ansar[j]
    j=j+1 }
    else if (s11$Away[i] == "Al-Ansar") {
      s11$PosA[i] <- Ansar[j]
      j=j+1}
  i=i+1}


##12
i=1
j=1
while (i<=182){
  if(s11$Home[i] == "Al-Ettifaq") {
    s11$PosH[i] <- Ettifaq[j]
    j=j+1 }
    else if (s11$Away[i] == "Al-Ettifaq") {
      s11$PosA[i] <- Ettifaq[j]
      j=j+1}
  i=i+1}

##13
i=1
j=1
while (i<=182){
  if(s11$Home[i] == "Al-Fateh") {
    s11$PosH[i] <- Fateh[j]
    j=j+1 }
    else if (s11$Away[i] == "Al-Fateh") {
      s11$PosA[i] <- Fateh[j]
      j=j+1}
  i=i+1}
##14
i=1
j=1
while (i<=182){
  if(s11$Home[i] == "Al-Shabab") {
    s11$PosH[i] <- Shabab[j]
    j=j+1 }
    else if (s11$Away[i] == "Al-Shabab") {
      s11$PosA[i] <- Shabab[j]
      j=j+1}
  i=i+1}

#Season2012
Ahli<- c(1,1,6,7,8,5,4,3,5,6,5,7,6,6,6,6,5,5,5,5,5,5,4,5,5,5)
Shabab<- c(1,2,1,1,1,3,2,5,4,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3)
Taawoun<- c(1,3,2,4,6,10,11,11,12,11,11,10,10,10,11,11,10,11,11,11,11,12,12,12,12,12)
Hilal<- c(1,4,9,6,7,4,3,2,2,2,2,2,2,2,1,2,2,2,2,2,2,2,2,2,2,2)
Ittihad<- c(1,5,4,2,3,2,5,4,6,5,6,8,8,7,7,7,7,7,7,7,7,7,7,7,7,7)
Raed<- c(1,6,12,10,10,7,8,7,8,9,9,9,9,9,9,9,9,9,9,9,8,9,9,8,8,8)
Hajer<- c(1,7,8,5,5,9,9,10,11,12,12,12,13,13,13,13,11,13,13,13,13,13,13,13,13,13)
Ettifaq<- c(1,8,11,9,9,12,10,12,9,8,7,5,4,5,5,5,6,6,6,6,6,6,6,6,6,6)
Fateh<- c(1,9,5,3,2,1,1,1,1,1,1,1,1,1,2,1,1,1,1,1,1,1,1,1,1,1)
Nassr<- c(1,10,3,8,4,6,6,6,3,4,4,4,5,4,4,4,4,4,4,4,4,4,5,4,4,4)
Wehda<- c(1,11,10,12,14,13,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14)
Faisaly<- c(1,12,14,14,13,14,13,13,13,13,13,13,12,12,10,12,12,12,12,12,12,11,11,11,11,11)
Najran<- c(1,13,13,13,13,8,7,8,7,7,8,6,7,8,8,8,8,8,8,8,9,8,8,9,9,10)
Shoulla<- c(1,14,7,11,12,11,12,9,10,10,10,11,11,11,12,10,13,10,10,10,10,10,10,10,10,9)


##1
i=1
j=1
while (i<=182){
  if(s12$Home[i] == "Najran") {
    s12$PosH[i] <- Najran[j]
    j=j+1 }
    else if (s12$Away[i] == "Najran") {
      s12$PosA[i] <- Najran[j]
      j=j+1}
  i=i+1}

##2
i=1
j=1
while (i<=182){
  if(s12$Home[i] == "Al-Wehda") {
    s12$PosH[i] <- Wehda[j]
    j=j+1 }
    else if (s12$Away[i] == "Al-Wehda") {
      s12$PosA[i] <- Wehda[j]
      j=j+1}
  i=i+1}
##3
i=1
j=1
while (i<=182){
  if(s12$Home[i] == "Al-Raed") {
    s12$PosH[i] <- Raed[j]
    j=j+1 }
    else if (s12$Away[i] == "Al-Raed") {
      s12$PosA[i] <- Raed[j]
      j=j+1}
  i=i+1}
##4
i=1
j=1
while (i<=182){
  if(s12$Home[i] == "Al-Ittihad") {
    s12$PosH[i] <- Ittihad[j]
    j=j+1 }
    else if (s12$Away[i] == "Al-Ittihad") {
      s12$PosA[i] <- Ittihad[j]
      j=j+1}
  i=i+1}

##5
i=1
j=1
while (i<=182){
  if(s12$Home[i] == "Al-Ahli") {
    s12$PosH[i] <- Ahli[j]
    j=j+1 }
    else if (s12$Away[i] == "Al-Ahli") {
      s12$PosA[i] <- Ahli[j]
      j=j+1}
  i=i+1}

##6
i=1
j=1
while (i<=182){
  if(s12$Home[i] == "Al-Hilal") {
    s12$PosH[i] <- Hilal[j]
    j=j+1 }
    else if (s12$Away[i] == "Al-Hilal") {
      s12$PosA[i] <- Hilal[j]
      j=j+1}
  i=i+1}

##7
i=1
j=1
while (i<=182){
  if(s12$Home[i] == "Al-Nassr") {
    s12$PosH[i] <- Nassr[j]
    j=j+1 }
    else if (s12$Away[i] == "Al-Nassr") {
      s12$PosA[i] <- Nassr[j]
      j=j+1}
  i=i+1}


##8
i=1
j=1
while (i<=182){
  if(s12$Home[i] == "Al-Taawoun") {
    s12$PosH[i] <- Taawoun[j]
    j=j+1 }
    else if (s12$Away[i] == "Al-Taawoun") {
      s12$PosA[i] <- Taawoun[j]
      j=j+1}
  i=i+1}

##9
i=1
j=1
while (i<=182){
  if(s12$Home[i] == "Al-Faisaly") {
    s12$PosH[i] <- Faisaly[j]
    j=j+1 }
    else if (s12$Away[i] == "Al-Faisaly") {
      s12$PosA[i] <- Faisaly[j]
      j=j+1}
  i=i+1}

##10
i=1
j=1
while (i<=182){
  if(s12$Home[i] == "Hajer") {
    s12$PosH[i] <- Hajer[j]
    j=j+1 }
    else if (s12$Away[i] == "Hajer") {
      s12$PosA[i] <- Hajer[j]
      j=j+1}
  i=i+1}

##11
i=1
j=1
while (i<=182){
  if(s12$Home[i] == "Al-Shoulla") {
    s12$PosH[i] <- Shoulla[j]
    j=j+1 }
    else if (s12$Away[i] == "Al-Shoulla") {
      s12$PosA[i] <- Shoulla[j]
      j=j+1}
  i=i+1}


##12
i=1
j=1
while (i<=182){
  if(s12$Home[i] == "Al-Ettifaq") {
    s12$PosH[i] <- Ettifaq[j]
    j=j+1 }
    else if (s12$Away[i] == "Al-Ettifaq") {
      s12$PosA[i] <- Ettifaq[j]
      j=j+1}
  i=i+1}

##13
i=1
j=1
while (i<=182){
  if(s12$Home[i] == "Al-Fateh") {
    s12$PosH[i] <- Fateh[j]
    j=j+1 }
    else if (s12$Away[i] == "Al-Fateh") {
      s12$PosA[i] <- Fateh[j]
      j=j+1}
  i=i+1}
##14
i=1
j=1
while (i<=182){
  if(s12$Home[i] == "Al-Shabab") {
    s12$PosH[i] <- Shabab[j]
    j=j+1 }
    else if (s12$Away[i] == "Al-Shabab") {
      s12$PosA[i] <- Shabab[j]
      j=j+1}
  i=i+1}

#Season2013
Ittihad<- c(1,1,5,3,6,4,6,6,7,7,6,7,8,7,7,6,6,6,6,7,7,6,6,6,6,6)
Hilal<- c(1,2,1,1,1,1,2,2,2,1,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2)
Ahli<- c(1,3,2,5,3,3,5,4,4,3,4,6,4,4,5,5,5,4,5,3,3,3,3,3,3,3)
Nassr<- c(1,4,3,2,2,2,1,1,1,2,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1)
Raed<- c(1,5,8,10,12,11,9,10,9,8,9,10,11,11,9,7,7,9,10,11,10,11,13,13,10,8)
Nahda<- c(1,6,12,13,14,13,13,13,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14)
Shoulla<- c(1,7,11,12,13,14,14,14,13,13,13,13,13,13,13,13,11,8,9,6,6,8,11,10,11,12)
Fateh<- c(1,8,4,7,8,7,7,7,8,9,8,9,9,9,10,10,9,7,8,10,11,7,7,7,7,9)
Taawoun<- c(1,9,10,6,5,8,8,8,6,6,5,4,5,6,4,4,3,3,3,5,5,5,5,5,5,5)
Ettifaq<- c(1,10,14,11,10,12,12,11,10,10,11,8,7,5,6,8,8,10,7,9,9,10,12,9,12,10)
Faisaly<- c(1,11,13,14,9,9,11,9,11,11,10,11,12,12,12,12,13,13,13,13,12,12,8,11,8,7)
Najran<- c(1,12,6,9,7,5,3,5,3,5,7,5,6,8,8,9,10,11,11,8,8,9,9,8,9,13)
Shabab<- c(1,13,9,4,4,6,4,3,5,4,3,3,3,3,3,3,4,5,4,4,4,4,4,4,4,4)
Orobah<- c(1,14,7,8,11,10,10,12,12,12,12,12,10,10,11,11,12,12,12,12,13,13,10,12,13,11)

##1
i=1
j=1
while (i<=182){
  if(s13$Home[i] == "Najran") {
    s13$PosH[i] <- Najran[j]
    j=j+1 }
    else if (s13$Away[i] == "Najran") {
      s13$PosA[i] <- Najran[j]
      j=j+1}
  i=i+1}

##2
i=1
j=1
while (i<=182){
  if(s13$Home[i] == "Al-Nahda") {
    s13$PosH[i] <- Nahda[j]
    j=j+1 }
    else if (s13$Away[i] == "Al-Nahda") {
      s13$PosA[i] <- Nahda[j]
      j=j+1}
  i=i+1}
##3
i=1
j=1
while (i<=182){
  if(s13$Home[i] == "Al-Raed") {
    s13$PosH[i] <- Raed[j]
    j=j+1 }
    else if (s13$Away[i] == "Al-Raed") {
      s13$PosA[i] <- Raed[j]
      j=j+1}
  i=i+1}
##4
i=1
j=1
while (i<=182){
  if(s13$Home[i] == "Al-Ittihad") {
    s13$PosH[i] <- Ittihad[j]
    j=j+1 }
    else if (s13$Away[i] == "Al-Ittihad") {
      s13$PosA[i] <- Ittihad[j]
      j=j+1}
  i=i+1}

##5
i=1
j=1
while (i<=182){
  if(s13$Home[i] == "Al-Ahli") {
    s13$PosH[i] <- Ahli[j]
    j=j+1 }
    else if (s13$Away[i] == "Al-Ahli") {
      s13$PosA[i] <- Ahli[j]
      j=j+1}
  i=i+1}

##6
i=1
j=1
while (i<=182){
  if(s13$Home[i] == "Al-Hilal") {
    s13$PosH[i] <- Hilal[j]
    j=j+1 }
    else if (s13$Away[i] == "Al-Hilal") {
      s13$PosA[i] <- Hilal[j]
      j=j+1}
  i=i+1}

##7
i=1
j=1
while (i<=182){
  if(s13$Home[i] == "Al-Nassr") {
    s13$PosH[i] <- Nassr[j]
    j=j+1 }
    else if (s13$Away[i] == "Al-Nassr") {
      s13$PosA[i] <- Nassr[j]
      j=j+1}
  i=i+1}


##8
i=1
j=1
while (i<=182){
  if(s13$Home[i] == "Al-Taawoun") {
    s13$PosH[i] <- Taawoun[j]
    j=j+1 }
    else if (s13$Away[i] == "Al-Taawoun") {
      s13$PosA[i] <- Taawoun[j]
      j=j+1}
  i=i+1}

##9
i=1
j=1
while (i<=182){
  if(s13$Home[i] == "Al-Faisaly") {
    s13$PosH[i] <- Faisaly[j]
    j=j+1 }
    else if (s13$Away[i] == "Al-Faisaly") {
      s13$PosA[i] <- Faisaly[j]
      j=j+1}
  i=i+1}

##10
i=1
j=1
while (i<=182){
  if(s13$Home[i] == "Al-Orobah") {
    s13$PosH[i] <- Orobah[j]
    j=j+1 }
    else if (s13$Away[i] == "Al-Orobah") {
      s13$PosA[i] <- Orobah[j]
      j=j+1}
  i=i+1}

##11
i=1
j=1
while (i<=182){
  if(s13$Home[i] == "Al-Shoulla") {
    s13$PosH[i] <- Shoulla[j]
    j=j+1 }
    else if (s13$Away[i] == "Al-Shoulla") {
      s13$PosA[i] <- Shoulla[j]
      j=j+1}
  i=i+1}


##12
i=1
j=1
while (i<=182){
  if(s13$Home[i] == "Al-Ettifaq") {
    s13$PosH[i] <- Ettifaq[j]
    j=j+1 }
    else if (s13$Away[i] == "Al-Ettifaq") {
      s13$PosA[i] <- Ettifaq[j]
      j=j+1}
  i=i+1}

##13
i=1
j=1
while (i<=182){
  if(s13$Home[i] == "Al-Fateh") {
    s13$PosH[i] <- Fateh[j]
    j=j+1 }
    else if (s13$Away[i] == "Al-Fateh") {
      s13$PosA[i] <- Fateh[j]
      j=j+1}
  i=i+1}
##14
i=1
j=1
while (i<=182){
  if(s13$Home[i] == "Al-Shabab") {
    s13$PosH[i] <- Shabab[j]
    j=j+1 }
    else if (s13$Away[i] == "Al-Shabab") {
      s13$PosA[i] <- Shabab[j]
      j=j+1}
  i=i+1}

#Season2014
Ahli<- c(1,1,5,7,6,6,5,5,5,3,3,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2)
Nassr<- c(1,2,2,2,1,1,1,3,2,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1)
Hilal<- c(1,3,1,4,4,3,3,4,4,5,5,4,4,4,3,4,5,5,4,4,4,3,3,3,3,3)
Shabab<- c(1,4,3,1,2,4,4,2,1,2,2,3,3,3,4,3,4,4,5,5,5,5,5,5,5,5)
Orobah<- c(1,5,7,6,7,7,7,8,8,9,9,11,12,11,12,12,13,13,13,13,13,13,14,13,13,14)
Faisaly<- c(1,6,6,5,5,5,6,6,6,6,6,6,6,6,6,7,7,7,6,6,6,6,6,6,6,6)
Ittihad<- c(1,7,4,3,3,2,2,1,3,4,4,5,5,5,5,5,3,3,3,3,3,4,4,4,4,4)
Taawoun<- c(1,8,13,12,9,10,10,10,10,11,10,8,9,8,8,6,6,6,7,7,7,7,8,8,9,10)
Fateh<- c(1,9,14,14,14,9,9,9,9,10,8,10,11,10,9,9,9,9,8,9,9,9,7,7,8,7)
Raed<- c(1,10,12,13,13,14,12,13,14,14,14,14,14,14,13,13,10,11,9,10,11,12,10,11,11,12)
Shoulla<- c(1,11,9,11,12,12,14,14,12,13,13,12,13,13,14,14,14,14,14,14,14,14,13,14,14,13)
Khaleej<- c(1,12,10,10,11,13,12,12,13,12,12,13,10,12,11,11,12,10,11,12,12,11,12,10,10,8)
Najran<- c(1,13,11,9,10,11,11,11,11,8,11,9,8,9,10,10,11,12,12,11,10,10,11,12,12,11)
Hajer<- c(1,14,8,8,8,8,8,7,7,7,7,7,7,7,7,8,8,8,10,8,8,8,9,9,7,9)

##1
i=1
j=1
while (i<=182){
  if(s14$Home[i] == "Najran") {
    s14$PosH[i] <- Najran[j]
    j=j+1 }
    else if (s14$Away[i] == "Najran") {
      s14$PosA[i] <- Najran[j]
      j=j+1}
  i=i+1}

##2
i=1
j=1
while (i<=182){
  if(s14$Home[i] == "Al-Khaleej") {
    s14$PosH[i] <- Khaleej[j]
    j=j+1 }
    else if (s14$Away[i] == "Al-Khaleej") {
      s14$PosA[i] <- Khaleej[j]
      j=j+1}
  i=i+1}
##3
i=1
j=1
while (i<=182){
  if(s14$Home[i] == "Al-Raed") {
    s14$PosH[i] <- Raed[j]
    j=j+1 }
    else if (s14$Away[i] == "Al-Raed") {
      s14$PosA[i] <- Raed[j]
      j=j+1}
  i=i+1}
##4
i=1
j=1
while (i<=182){
  if(s14$Home[i] == "Al-Ittihad") {
    s14$PosH[i] <- Ittihad[j]
    j=j+1 }
    else if (s14$Away[i] == "Al-Ittihad") {
      s14$PosA[i] <- Ittihad[j]
      j=j+1}
  i=i+1}

##5
i=1
j=1
while (i<=182){
  if(s14$Home[i] == "Al-Ahli") {
    s14$PosH[i] <- Ahli[j]
    j=j+1 }
    else if (s14$Away[i] == "Al-Ahli") {
      s14$PosA[i] <- Ahli[j]
      j=j+1}
  i=i+1}

##6
i=1
j=1
while (i<=182){
  if(s14$Home[i] == "Al-Hilal") {
    s14$PosH[i] <- Hilal[j]
    j=j+1 }
    else if (s14$Away[i] == "Al-Hilal") {
      s14$PosA[i] <- Hilal[j]
      j=j+1}
  i=i+1}

##7
i=1
j=1
while (i<=182){
  if(s14$Home[i] == "Al-Nassr") {
    s14$PosH[i] <- Nassr[j]
    j=j+1 }
    else if (s14$Away[i] == "Al-Nassr") {
      s14$PosA[i] <- Nassr[j]
      j=j+1}
  i=i+1}


##8
i=1
j=1
while (i<=182){
  if(s14$Home[i] == "Al-Taawoun") {
    s14$PosH[i] <- Taawoun[j]
    j=j+1 }
    else if (s14$Away[i] == "Al-Taawoun") {
      s14$PosA[i] <- Taawoun[j]
      j=j+1}
  i=i+1}

##9
i=1
j=1
while (i<=182){
  if(s14$Home[i] == "Al-Faisaly") {
    s14$PosH[i] <- Faisaly[j]
    j=j+1 }
    else if (s14$Away[i] == "Al-Faisaly") {
      s14$PosA[i] <- Faisaly[j]
      j=j+1}
  i=i+1}

##10
i=1
j=1
while (i<=182){
  if(s14$Home[i] == "Al-Orobah") {
    s14$PosH[i] <- Orobah[j]
    j=j+1 }
    else if (s14$Away[i] == "Al-Orobah") {
      s14$PosA[i] <- Orobah[j]
      j=j+1}
  i=i+1}

##11
i=1
j=1
while (i<=182){
  if(s14$Home[i] == "Al-Shoulla") {
    s14$PosH[i] <- Shoulla[j]
    j=j+1 }
    else if (s14$Away[i] == "Al-Shoulla") {
      s14$PosA[i] <- Shoulla[j]
      j=j+1}
  i=i+1}


##12
i=1
j=1
while (i<=182){
  if(s14$Home[i] == "Hajer") {
    s14$PosH[i] <- Hajer[j]
    j=j+1 }
    else if (s14$Away[i] == "Hajer") {
      s14$PosA[i] <- Hajer[j]
      j=j+1}
  i=i+1}

##13
i=1
j=1
while (i<=182){
  if(s14$Home[i] == "Al-Fateh") {
    s14$PosH[i] <- Fateh[j]
    j=j+1 }
    else if (s14$Away[i] == "Al-Fateh") {
      s14$PosA[i] <- Fateh[j]
      j=j+1}
  i=i+1}
##14
i=1
j=1
while (i<=182){
  if(s14$Home[i] == "Al-Shabab") {
    s14$PosH[i] <- Shabab[j]
    j=j+1 }
    else if (s14$Away[i] == "Al-Shabab") {
      s14$PosA[i] <- Shabab[j]
      j=j+1}
  i=i+1}


#Season2015
Shabab<- c(1,1,1,4,3,4,4,5,5,5,6,8,9,6,5,5,5,5,5,5,5,5,5,6,6,6)
Fateh<- c(1,2,7,7,6,8,9,7,6,7,5,5,5,5,7,7,7,6,8,9,7,6,6,5,5,5)
Hilal<- c(1,3,2,1,1,3,1,1,1,1,1,2,2,2,1,1,1,1,1,2,2,2,2,2,2,2)
Ittihad<- c(1,4,3,5,4,2,3,3,3,4,3,3,4,3,3,3,3,3,3,3,3,3,3,3,3,3)
Qadisiyah<- c(1,5,6,8,8,9,11,11,11,11,12,12,11,11,11,11,11,11,13,12,13,13,11,12,12,11)
Ahli<- c(1,6,4,2,2,1,2,2,2,2,2,1,1,1,2,2,2,2,2,1,1,1,1,1,1,1)
Nassr<- c(1,7,8,6,7,6,6,8,8,6,8,7,6,8,6,6,6,7,7,8,9,8,8,8,8,8)
Taawoun<- c(1,8,5,3,5,5,5,4,4,3,4,4,3,4,4,4,4,4,4,4,4,4,4,4,4,4)
Hajer<- c(1,9,11,10,11,11,12,13,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14)
Najran<- c(1,10,9,11,13,14,14,14,13,12,13,13,13,13,13,13,12,12,10,11,11,11,12,13,13,13)
Faisaly<- c(1,11,12,9,10,7,7,9,9,9,9,9,8,9,9,9,9,8,6,7,8,9,9,9,9,9)
Raed<- c(1,12,13,14,14,12,13,10,10,10,10,11,12,12,12,12,13,13,12,13,12,12,13,11,11,12)
Khaleej<- c(1,13,14,13,9,10,8,6,7,8,7,6,7,7,8,8,8,9,9,6,6,7,7,7,7,7)
Wehda<- c(1,14,10,12,12,13,10,12,12,13,11,10,10,10,10,10,10,10,11,10,10,10,10,10,10,10)

##1
i=1
j=1
while (i<=182){
  if(s15$Home[i] == "Najran") {
    s15$PosH[i] <- Najran[j]
    j=j+1 }
    else if (s15$Away[i] == "Najran") {
      s15$PosA[i] <- Najran[j]
      j=j+1}
  i=i+1}

##2
i=1
j=1
while (i<=182){
  if(s15$Home[i] == "Al-Khaleej") {
    s15$PosH[i] <- Khaleej[j]
    j=j+1 }
    else if (s15$Away[i] == "Al-Khaleej") {
      s15$PosA[i] <- Khaleej[j]
      j=j+1}
  i=i+1}
##3
i=1
j=1
while (i<=182){
  if(s15$Home[i] == "Al-Raed") {
    s15$PosH[i] <- Raed[j]
    j=j+1 }
    else if (s15$Away[i] == "Al-Raed") {
      s15$PosA[i] <- Raed[j]
      j=j+1}
  i=i+1}
##4
i=1
j=1
while (i<=182){
  if(s15$Home[i] == "Al-Ittihad") {
    s15$PosH[i] <- Ittihad[j]
    j=j+1 }
    else if (s15$Away[i] == "Al-Ittihad") {
      s15$PosA[i] <- Ittihad[j]
      j=j+1}
  i=i+1}

##5
i=1
j=1
while (i<=182){
  if(s15$Home[i] == "Al-Ahli") {
    s15$PosH[i] <- Ahli[j]
    j=j+1 }
    else if (s15$Away[i] == "Al-Ahli") {
      s15$PosA[i] <- Ahli[j]
      j=j+1}
  i=i+1}

##6
i=1
j=1
while (i<=182){
  if(s15$Home[i] == "Al-Hilal") {
    s15$PosH[i] <- Hilal[j]
    j=j+1 }
    else if (s15$Away[i] == "Al-Hilal") {
      s15$PosA[i] <- Hilal[j]
      j=j+1}
  i=i+1}

##7
i=1
j=1
while (i<=182){
  if(s15$Home[i] == "Al-Nassr") {
    s15$PosH[i] <- Nassr[j]
    j=j+1 }
    else if (s15$Away[i] == "Al-Nassr") {
      s15$PosA[i] <- Nassr[j]
      j=j+1}
  i=i+1}


##8
i=1
j=1
while (i<=182){
  if(s15$Home[i] == "Al-Taawoun") {
    s15$PosH[i] <- Taawoun[j]
    j=j+1 }
    else if (s15$Away[i] == "Al-Taawoun") {
      s15$PosA[i] <- Taawoun[j]
      j=j+1}
  i=i+1}

##9
i=1
j=1
while (i<=182){
  if(s15$Home[i] == "Al-Faisaly") {
    s15$PosH[i] <- Faisaly[j]
    j=j+1 }
    else if (s15$Away[i] == "Al-Faisaly") {
      s15$PosA[i] <- Faisaly[j]
      j=j+1}
  i=i+1}

##10
i=1
j=1
while (i<=182){
  if(s15$Home[i] == "Al-Qadisiyah") {
    s15$PosH[i] <- Qadisiyah[j]
    j=j+1 }
    else if (s15$Away[i] == "Al-Qadisiyah") {
      s15$PosA[i] <- Qadisiyah[j]
      j=j+1}
  i=i+1}

##11
i=1
j=1
while (i<=182){
  if(s15$Home[i] == "Al-Wehda") {
    s15$PosH[i] <- Wehda[j]
    j=j+1 }
    else if (s15$Away[i] == "Al-Wehda") {
      s15$PosA[i] <- Wehda[j]
      j=j+1}
  i=i+1}


##12
i=1
j=1
while (i<=182){
  if(s15$Home[i] == "Hajer") {
    s15$PosH[i] <- Hajer[j]
    j=j+1 }
    else if (s15$Away[i] == "Hajer") {
      s15$PosA[i] <- Hajer[j]
      j=j+1}
  i=i+1}

##13
i=1
j=1
while (i<=182){
  if(s15$Home[i] == "Al-Fateh") {
    s15$PosH[i] <- Fateh[j]
    j=j+1 }
    else if (s15$Away[i] == "Al-Fateh") {
      s15$PosA[i] <- Fateh[j]
      j=j+1}
  i=i+1}
##14
i=1
j=1
while (i<=182){
  if(s15$Home[i] == "Al-Shabab") {
    s15$PosH[i] <- Shabab[j]
    j=j+1 }
    else if (s15$Away[i] == "Al-Shabab") {
      s15$PosA[i] <- Shabab[j]
      j=j+1}
  i=i+1}

#Season2016
Ahli<- c(1,1,1,3,5,3,5,5,5,3,4,4,4,3,2,2,2,2,2,4,3,3,3,4,4,3)
Nassr<- c(1,2,8,5,6,5,3,3,3,2,3,3,3,4,4,3,4,3,3,2,2,2,2,2,3,2)
Faisaly<- c(1,3,4,6,4,7,9,11,10,9,11,11,13,12,12,9,11,10,11,11,11,10,9,9,9,9)
Hilal<- c(1,4,2,4,3,2,1,2,2,1,1,1,1,2,1,1,1,1,1,1,1,1,1,1,1,1)
Ittihad<- c(1,5,3,1,1,1,2,1,1,4,2,2,2,1,3,4,3,4,4,3,4,4,4,3,2,4)
Wehda<- c(1,6,9,11,12,12,10,8,8,8,9,9,11,13,13,12,13,14,14,12,12,13,14,14,14,14)
Shabab<- c(1,7,11,8,8,6,4,4,4,5,5,5,5,5,5,5,5,5,5,5,5,6,5,5,6,7)
Qadisiyah<- c(1,8,10,12,13,13,13,13,13,12,14,12,12,10,9,10,9,11,9,9,7,8,10,10,12,11)
Taawoun<- c(1,9,13,10,11,11,11,10,11,10,8,7,7,8,7,7,8,7,8,6,8,5,6,7,7,6)
Raed<- c(1,10,5,9,7,9,7,6,7,7,7,8,8,7,8,8,7,9,6,7,6,7,7,6,5,5)
Khaleej<- c(1,11,12,13,9,10,12,12,12,13,12,14,10,11,11,11,12,13,13,14,14,12,13,13,13,13)
Batin<- c(1,12,7,7,10,8,8,9,9,11,10,10,9,9,10,13,10,9,10,10,10,11,11,12,11,12)
Fateh<- c(1,13,14,14,14,14,14,14,14,14,13,13,14,14,14,14,14,12,12,13,13,14,12,11,10,10)
Ettifaq<- c(1,14,6,2,2,4,6,7,6,6,6,6,6,6,6,6,6,6,7,8,9,9,8,8,8,8)



##1
i=1
j=1
while (i<=182){
  if(s16$Home[i] == "Al-Batin") {
    s16$PosH[i] <- Batin[j]
    j=j+1 }
    else if (s16$Away[i] == "Al-Batin") {
      s16$PosA[i] <- Batin[j]
      j=j+1}
  i=i+1}

##2
i=1
j=1
while (i<=182){
  if(s16$Home[i] == "Al-Khaleej") {
    s16$PosH[i] <- Khaleej[j]
    j=j+1 }
    else if (s16$Away[i] == "Al-Khaleej") {
      s16$PosA[i] <- Khaleej[j]
      j=j+1}
  i=i+1}
##3
i=1
j=1
while (i<=182){
  if(s16$Home[i] == "Al-Raed") {
    s16$PosH[i] <- Raed[j]
    j=j+1 }
    else if (s16$Away[i] == "Al-Raed") {
      s16$PosA[i] <- Raed[j]
      j=j+1}
  i=i+1}
##4
i=1
j=1
while (i<=182){
  if(s16$Home[i] == "Al-Ittihad") {
    s16$PosH[i] <- Ittihad[j]
    j=j+1 }
    else if (s16$Away[i] == "Al-Ittihad") {
      s16$PosA[i] <- Ittihad[j]
      j=j+1}
  i=i+1}

##5
i=1
j=1
while (i<=182){
  if(s16$Home[i] == "Al-Ahli") {
    s16$PosH[i] <- Ahli[j]
    j=j+1 }
    else if (s16$Away[i] == "Al-Ahli") {
      s16$PosA[i] <- Ahli[j]
      j=j+1}
  i=i+1}

##6
i=1
j=1
while (i<=182){
  if(s16$Home[i] == "Al-Hilal") {
    s16$PosH[i] <- Hilal[j]
    j=j+1 }
    else if (s16$Away[i] == "Al-Hilal") {
      s16$PosA[i] <- Hilal[j]
      j=j+1}
  i=i+1}

##7
i=1
j=1
while (i<=182){
  if(s16$Home[i] == "Al-Nassr") {
    s16$PosH[i] <- Nassr[j]
    j=j+1 }
    else if (s16$Away[i] == "Al-Nassr") {
      s16$PosA[i] <- Nassr[j]
      j=j+1}
  i=i+1}


##8
i=1
j=1
while (i<=182){
  if(s16$Home[i] == "Al-Taawoun") {
    s16$PosH[i] <- Taawoun[j]
    j=j+1 }
    else if (s16$Away[i] == "Al-Taawoun") {
      s16$PosA[i] <- Taawoun[j]
      j=j+1}
  i=i+1}

##9
i=1
j=1
while (i<=182){
  if(s16$Home[i] == "Al-Faisaly") {
    s16$PosH[i] <- Faisaly[j]
    j=j+1 }
    else if (s16$Away[i] == "Al-Faisaly") {
      s16$PosA[i] <- Faisaly[j]
      j=j+1}
  i=i+1}

##10
i=1
j=1
while (i<=182){
  if(s16$Home[i] == "Al-Qadisiyah") {
    s16$PosH[i] <- Qadisiyah[j]
    j=j+1 }
    else if (s16$Away[i] == "Al-Qadisiyah") {
      s16$PosA[i] <- Qadisiyah[j]
      j=j+1}
  i=i+1}

##11
i=1
j=1
while (i<=182){
  if(s16$Home[i] == "Al-Wehda") {
    s16$PosH[i] <- Wehda[j]
    j=j+1 }
    else if (s16$Away[i] == "Al-Wehda") {
      s16$PosA[i] <- Wehda[j]
      j=j+1}
  i=i+1}


##12
i=1
j=1
while (i<=182){
  if(s16$Home[i] == "Al-Ettifaq") {
    s16$PosH[i] <- Ettifaq[j]
    j=j+1 }
    else if (s16$Away[i] == "Al-Ettifaq") {
      s16$PosA[i] <- Ettifaq[j]
      j=j+1}
  i=i+1}

##13
i=1
j=1
while (i<=182){
  if(s16$Home[i] == "Al-Fateh") {
    s16$PosH[i] <- Fateh[j]
    j=j+1 }
    else if (s16$Away[i] == "Al-Fateh") {
      s16$PosA[i] <- Fateh[j]
      j=j+1}
  i=i+1}
##14
i=1
j=1
while (i<=182){
  if(s16$Home[i] == "Al-Shabab") {
    s16$PosH[i] <- Shabab[j]
    j=j+1 }
    else if (s16$Away[i] == "Al-Shabab") {
      s16$PosA[i] <- Shabab[j]
      j=j+1}
  i=i+1}

```

workspace has been saved (CapstoneV2)

```{r}
#Season2017
Taawoun<- c(1,1,6,9,7,10,10,7,7,9,9,7,8,7,7,9,7,8,7,5,5,5,5,6,8,5)
Nassr<- c(1,2,3,7,5,5,5,4,3,4,3,4,3,3,3,4,3,4,3,4,3,3,4,3,3,3)
Batin<- c(1,3,1,2,1,3,3,3,5,5,5,5,5,6,6,6,8,9,10,10,11,11,11,11,11,11)
Hilal<- c(1,4,2,1,2,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1)
Qadisiyah<- c(1,5,11,5,4,7,8,9,9,7,8,9,10,8,8,10,12,12,12,12,12,13,12,12,12,12)
Ettifaq<- c(1,6,4,11,8,12,13,13,11,10,10,10,11,13,13,12,10,11,11,11,10,10,9,9,6,9)
Ohod<- c(1,7,10,12,11,13,12,12,14,14,12,13,12,12,12,13,13,13,13,13,13,12,13,13,14,14)
Ahli<- c(1,8,5,3,6,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2)
Raed<- c(1,9,12,14,14,14,14,14,13,13,14,14,14,14,14,14,14,14,14,14,14,14,14,14,13,13)
Shabab<- c(1,10,7,6,9,9,9,10,10,11,11,11,9,10,10,7,6,5,5,8,8,9,10,10,9,10)
Fayha<- c(1,11,13,13,13,11,11,11,12,12,13,12,13,11,11,8,9,7,6,7,6,6,6,7,7,7)
Ittihad<- c(1,12,8,10,10,6,7,8,8,6,7,8,6,5,5,5,5,6,8,6,7,7,7,8,10,8)
Faisaly<- c(1,13,9,4,3,4,4,5,4,3,4,3,4,4,4,3,4,3,4,3,4,4,3,4,5,6)
Fateh<- c(1,14,14,8,12,8,6,6,6,8,6,6,7,9,9,11,11,10,9,9,9,8,8,5,4,4)



##1
i=1
j=1
while (i<=182){
  if(s17$Home[i] == "Al-Batin") {
    s17$PosH[i] <- Batin[j]
    j=j+1 }
    else if (s17$Away[i] == "Al-Batin") {
      s17$PosA[i] <- Batin[j]
      j=j+1}
  i=i+1}

##2
i=1
j=1
while (i<=182){
  if(s17$Home[i] == "Ohod") {
    s17$PosH[i] <- Ohod[j]
    j=j+1 }
    else if (s17$Away[i] == "Ohod") {
      s17$PosA[i] <- Ohod[j]
      j=j+1}
  i=i+1}
##3
i=1
j=1
while (i<=182){
  if(s17$Home[i] == "Al-Raed") {
    s17$PosH[i] <- Raed[j]
    j=j+1 }
    else if (s17$Away[i] == "Al-Raed") {
      s17$PosA[i] <- Raed[j]
      j=j+1}
  i=i+1}
##4
i=1
j=1
while (i<=182){
  if(s17$Home[i] == "Al-Ittihad") {
    s17$PosH[i] <- Ittihad[j]
    j=j+1 }
    else if (s17$Away[i] == "Al-Ittihad") {
      s17$PosA[i] <- Ittihad[j]
      j=j+1}
  i=i+1}

##5
i=1
j=1
while (i<=182){
  if(s17$Home[i] == "Al-Ahli") {
    s17$PosH[i] <- Ahli[j]
    j=j+1 }
    else if (s17$Away[i] == "Al-Ahli") {
      s17$PosA[i] <- Ahli[j]
      j=j+1}
  i=i+1}

##6
i=1
j=1
while (i<=182){
  if(s17$Home[i] == "Al-Hilal") {
    s17$PosH[i] <- Hilal[j]
    j=j+1 }
    else if (s17$Away[i] == "Al-Hilal") {
      s17$PosA[i] <- Hilal[j]
      j=j+1}
  i=i+1}

##7
i=1
j=1
while (i<=182){
  if(s17$Home[i] == "Al-Nassr") {
    s17$PosH[i] <- Nassr[j]
    j=j+1 }
    else if (s17$Away[i] == "Al-Nassr") {
      s17$PosA[i] <- Nassr[j]
      j=j+1}
  i=i+1}


##8
i=1
j=1
while (i<=182){
  if(s17$Home[i] == "Al-Taawoun") {
    s17$PosH[i] <- Taawoun[j]
    j=j+1 }
    else if (s17$Away[i] == "Al-Taawoun") {
      s17$PosA[i] <- Taawoun[j]
      j=j+1}
  i=i+1}

##9
i=1
j=1
while (i<=182){
  if(s17$Home[i] == "Al-Faisaly") {
    s17$PosH[i] <- Faisaly[j]
    j=j+1 }
    else if (s17$Away[i] == "Al-Faisaly") {
      s17$PosA[i] <- Faisaly[j]
      j=j+1}
  i=i+1}

##10
i=1
j=1
while (i<=182){
  if(s17$Home[i] == "Al-Qadisiyah") {
    s17$PosH[i] <- Qadisiyah[j]
    j=j+1 }
    else if (s17$Away[i] == "Al-Qadisiyah") {
      s17$PosA[i] <- Qadisiyah[j]
      j=j+1}
  i=i+1}

##11
i=1
j=1
while (i<=182){
  if(s17$Home[i] == "Al-Fayha") {
    s17$PosH[i] <- Fayha[j]
    j=j+1 }
    else if (s17$Away[i] == "Al-Fayha") {
      s17$PosA[i] <- Fayha[j]
      j=j+1}
  i=i+1}


##12
i=1
j=1
while (i<=182){
  if(s17$Home[i] == "Al-Ettifaq") {
    s17$PosH[i] <- Ettifaq[j]
    j=j+1 }
    else if (s17$Away[i] == "Al-Ettifaq") {
      s17$PosA[i] <- Ettifaq[j]
      j=j+1}
  i=i+1}

##13
i=1
j=1
while (i<=182){
  if(s17$Home[i] == "Al-Fateh") {
    s17$PosH[i] <- Fateh[j]
    j=j+1 }
    else if (s17$Away[i] == "Al-Fateh") {
      s17$PosA[i] <- Fateh[j]
      j=j+1}
  i=i+1}
##14
i=1
j=1
while (i<=182){
  if(s17$Home[i] == "Al-Shabab") {
    s17$PosH[i] <- Shabab[j]
    j=j+1 }
    else if (s17$Away[i] == "Al-Shabab") {
      s17$PosA[i] <- Shabab[j]
      j=j+1}
  i=i+1}



#Season2018 (Has to additional teams whcih means:
# Teams = 16 instead of 14
# Games = 240 instead of 182 (30 fixtures not 26)
Nassr<- c(1,1,3,2,2,1,1,2,3,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,1,1,2,1,1)
Hilal<- c(1,2,1,1,1,2,2,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,2,2,1,2,2)
Taawoun<- c(1,9,7,7,7,7,6,6,7,7,6,5,4,3,4,4,6,6,5,6,5,4,4,4,4,4,4,4,4,4)
Ahli<- c(1,6,5,3,4,3,3,3,2,3,3,3,3,4,5,5,4,4,4,3,4,5,5,5,5,5,5,5,5,5)
Shabab<- c(1,3,2,5,5,5,8,7,5,4,5,6,6,5,3,3,3,3,3,4,3,3,3,3,3,3,3,3,3,3)
Faisaly<- c(1,5,12,9,8,11,12,10,8,8,9,9,8,9,7,7,7,8,8,9,8,8,8,8,7,6,7,6,6,6)
Wehda<- c(1,13,10,6,6,4,4,4,4,5,4,4,5,6,6,6,5,5,6,5,6,6,6,6,6,7,6,7,7,7)
Raed<- c(1,8,13,13,13,9,10,11,10,9,11,8,10,11,11,9,9,10,10,11,10,10,10,10,10,10,10,10,9,9)
Fateh<- c(1,10,9,11,10,8,7,8,9,10,8,10,7,8,10,11,11,9,11,8,7,7,7,7,8,8,8,8,8,8)
Ittihad<- c(1,16,16,16,15,16,16,16,16,16,16,16,16,15,15,15,15,15,15,15,15,15,15,14,13,13,13,12,11,10)
Ettifaq<- c(1,7,6,4,3,6,5,5,6,6,7,7,9,7,9,8,8,7,7,7,9,9,9,9,9,9,9,9,10,11)
Fayha<- c(1,15,14,12,16,14,14,13,12,11,10,11,12,13,12,12,13,14,14,14,14,14,13,15,15,15,14,13,13,13)
Hazem<- c(1,11,8,8,11,10,9,9,11,12,13,13,13,12,13,13,12,13,12,12,12,12,12,12,12,11,12,11,12,12)
Qadisiyah<- c(1,12,4,10,9,12,11,12,15,14,12,12,11,10,8,10,10,11,9,10,11,11,11,11,11,12,11,14,14,14)
Batin<- c(1,4,11,14,12,13,13,14,13,13,14,14,14,14,14,14,14,12,13,13,13,13,14,13,14,14,15,15,15,15)
Ohod<- c(1,14,15,15,14,15,15,15,14,15,15,15,15,16,16,16,16,16,16,16,16,16,16,16,16,16,16,16,16,16)


##1
i=1
j=1
while (i<=240){
  if(s18$Home[i] == "Al-Batin") {
    s18$PosH[i] <- Batin[j]
    j=j+1 }
    else if (s18$Away[i] == "Al-Batin") {
      s18$PosA[i] <- Batin[j]
      j=j+1}
  i=i+1}

##2
i=1
j=1
while (i<=240){
  if(s18$Home[i] == "Ohod") {
    s18$PosH[i] <- Ohod[j]
    j=j+1 }
    else if (s18$Away[i] == "Ohod") {
      s18$PosA[i] <- Ohod[j]
      j=j+1}
  i=i+1}
##3
i=1
j=1
while (i<=240){
  if(s18$Home[i] == "Al-Raed") {
    s18$PosH[i] <- Raed[j]
    j=j+1 }
    else if (s18$Away[i] == "Al-Raed") {
      s18$PosA[i] <- Raed[j]
      j=j+1}
  i=i+1}
##4
i=1
j=1
while (i<=240){
  if(s18$Home[i] == "Al-Ittihad") {
    s18$PosH[i] <- Ittihad[j]
    j=j+1 }
    else if (s18$Away[i] == "Al-Ittihad") {
      s18$PosA[i] <- Ittihad[j]
      j=j+1}
  i=i+1}

##5
i=1
j=1
while (i<=240){
  if(s18$Home[i] == "Al-Ahli") {
    s18$PosH[i] <- Ahli[j]
    j=j+1 }
    else if (s18$Away[i] == "Al-Ahli") {
      s18$PosA[i] <- Ahli[j]
      j=j+1}
  i=i+1}

##6
i=1
j=1
while (i<=240){
  if(s18$Home[i] == "Al-Hilal") {
    s18$PosH[i] <- Hilal[j]
    j=j+1 }
    else if (s18$Away[i] == "Al-Hilal") {
      s18$PosA[i] <- Hilal[j]
      j=j+1}
  i=i+1}

##7
i=1
j=1
while (i<=240){
  if(s18$Home[i] == "Al-Nassr") {
    s18$PosH[i] <- Nassr[j]
    j=j+1 }
    else if (s18$Away[i] == "Al-Nassr") {
      s18$PosA[i] <- Nassr[j]
      j=j+1}
  i=i+1}


##8
i=1
j=1
while (i<=240){
  if(s18$Home[i] == "Al-Taawoun") {
    s18$PosH[i] <- Taawoun[j]
    j=j+1 }
    else if (s18$Away[i] == "Al-Taawoun") {
      s18$PosA[i] <- Taawoun[j]
      j=j+1}
  i=i+1}

##9
i=1
j=1
while (i<=240){
  if(s18$Home[i] == "Al-Faisaly") {
    s18$PosH[i] <- Faisaly[j]
    j=j+1 }
    else if (s18$Away[i] == "Al-Faisaly") {
      s18$PosA[i] <- Faisaly[j]
      j=j+1}
  i=i+1}

##10
i=1
j=1
while (i<=240){
  if(s18$Home[i] == "Al-Qadisiyah") {
    s18$PosH[i] <- Qadisiyah[j]
    j=j+1 }
    else if (s18$Away[i] == "Al-Qadisiyah") {
      s18$PosA[i] <- Qadisiyah[j]
      j=j+1}
  i=i+1}

##11
i=1
j=1
while (i<=240){
  if(s18$Home[i] == "Al-Fayha") {
    s18$PosH[i] <- Fayha[j]
    j=j+1 }
    else if (s18$Away[i] == "Al-Fayha") {
      s18$PosA[i] <- Fayha[j]
      j=j+1}
  i=i+1}


##12
i=1
j=1
while (i<=240){
  if(s18$Home[i] == "Al-Ettifaq") {
    s18$PosH[i] <- Ettifaq[j]
    j=j+1 }
    else if (s18$Away[i] == "Al-Ettifaq") {
      s18$PosA[i] <- Ettifaq[j]
      j=j+1}
  i=i+1}

##13
i=1
j=1
while (i<=240){
  if(s18$Home[i] == "Al-Fateh") {
    s18$PosH[i] <- Fateh[j]
    j=j+1 }
    else if (s18$Away[i] == "Al-Fateh") {
      s18$PosA[i] <- Fateh[j]
      j=j+1}
  i=i+1}
##14
i=1
j=1
while (i<=240){
  if(s18$Home[i] == "Al-Shabab") {
    s18$PosH[i] <- Shabab[j]
    j=j+1 }
    else if (s18$Away[i] == "Al-Shabab") {
      s18$PosA[i] <- Shabab[j]
      j=j+1}
  i=i+1}

##15
i=1
j=1
while (i<=240){
  if(s18$Home[i] == "Al-Hazem") {
    s18$PosH[i] <- Hazem[j]
    j=j+1 }
    else if (s18$Away[i] == "Al-Hazem") {
      s18$PosA[i] <- Hazem[j]
      j=j+1}
  i=i+1}


##16
i=1
j=1
while (i<=240){
  if(s18$Home[i] == "Al-Wehda") {
    s18$PosH[i] <- Wehda[j]
    j=j+1 }
    else if (s18$Away[i] == "Al-Wehda") {
      s18$PosA[i] <- Wehda[j]
      j=j+1}
  i=i+1}


# Season2019 (until COVID19)
Nassr<- c(1,3,3,6,2,6,5,5,2,2,3,2,2,1,2,1,2,2,2,2,2)
Hilal<- c(1,1,1,1,1,1,1,1,1,1,1,1,1,2,1,2,1,1,1,1,1)
Taawoun<- c(1,8,12,4,9,8,6,7,7,5,4,6,4,7,5,5,4,5,6,6,7)
Ahli<- c(1,6,5,5,11,5,3,3,5,3,2,4,3,4,3,3,3,3,3,3,3)
Shabab<- c(1,5,6,10,7,12,9,6,3,6,7,9,10,9,9,9,7,8,8,8,8)
Faisaly<- c(1,10,10,2,5,2,4,4,6,4,6,5,5,8,8,7,8,7,7,7,6)
Wehda<- c(1,16,14,9,12,4,2,2,4,7,5,3,6,3,6,4,6,4,4,4,4)
Raed<- c(1,14,15,15,15,14,13,14,13,10,10,7,7,6,4,6,5,6,5,5,5)
Fateh<- c(1,13,13,16,16,16,16,15,15,15,15,16,14,14,14,14,15,15,16,14,14)
Ittihad<- c(1,2,2,8,4,3,8,9,11,13,12,13,13,13,13,13,12,13,13,13,12)
Ettifaq<- c(1,4,9,7,3,11,12,12,10,11,13,11,12,10,10,11,11,11,12,11,10)
Fayha<- c(1,11,7,11,6,13,14,13,12,12,11,12,9,11,11,10,10,10,11,10,9)
Hazem<- c(1,7,11,14,14,10,7,8,8,8,8,10,11,12,12,12,13,12,10,12,13)
Adalah<- c(1,9,4,3,8,7,10,11,14,14,14,14,15,15,15,15,14,14,15,15,16)
Abha<- c(1,12,8,12,10,9,11,10,9,9,9,8,8,5,7,8,9,9,9,9,11)
Damac<- c(1,15,16,13,13,15,15,16,16,16,16,15,16,16,16,16,16,16,14,16,15)

##1
i=1
j=1
while (i<=165){
  if(s19$Home[i] == "Al-Adalah") {
    s19$PosH[i] <- Adalah[j]
    j=j+1 }
    else if (s19$Away[i] == "Al-Adalah") {
      s19$PosA[i] <- Adalah[j]
      j=j+1}
  i=i+1}

##2
i=1
j=1
while (i<=165){
  if(s19$Home[i] == "Abha") {
    s19$PosH[i] <- Abha[j]
    j=j+1 }
    else if (s19$Away[i] == "Abha") {
      s19$PosA[i] <- Abha[j]
      j=j+1}
  i=i+1}
##3
i=1
j=1
while (i<=165){
  if(s19$Home[i] == "Al-Raed") {
    s19$PosH[i] <- Raed[j]
    j=j+1 }
    else if (s19$Away[i] == "Al-Raed") {
      s19$PosA[i] <- Raed[j]
      j=j+1}
  i=i+1}
##4
i=1
j=1
while (i<=165){
  if(s19$Home[i] == "Al-Ittihad") {
    s19$PosH[i] <- Ittihad[j]
    j=j+1 }
    else if (s19$Away[i] == "Al-Ittihad") {
      s19$PosA[i] <- Ittihad[j]
      j=j+1}
  i=i+1}

##5
i=1
j=1
while (i<=165){
  if(s19$Home[i] == "Al-Ahli") {
    s19$PosH[i] <- Ahli[j]
    j=j+1 }
    else if (s19$Away[i] == "Al-Ahli") {
      s19$PosA[i] <- Ahli[j]
      j=j+1}
  i=i+1}

##6
i=1
j=1
while (i<=165){
  if(s19$Home[i] == "Al-Hilal") {
    s19$PosH[i] <- Hilal[j]
    j=j+1 }
    else if (s19$Away[i] == "Al-Hilal") {
      s19$PosA[i] <- Hilal[j]
      j=j+1}
  i=i+1}

##7
i=1
j=1
while (i<=165){
  if(s19$Home[i] == "Al-Nassr") {
    s19$PosH[i] <- Nassr[j]
    j=j+1 }
    else if (s19$Away[i] == "Al-Nassr") {
      s19$PosA[i] <- Nassr[j]
      j=j+1}
  i=i+1}


##8
i=1
j=1
while (i<=165){
  if(s19$Home[i] == "Al-Taawoun") {
    s19$PosH[i] <- Taawoun[j]
    j=j+1 }
    else if (s19$Away[i] == "Al-Taawoun") {
      s19$PosA[i] <- Taawoun[j]
      j=j+1}
  i=i+1}

##9
i=1
j=1
while (i<=165){
  if(s19$Home[i] == "Al-Faisaly") {
    s19$PosH[i] <- Faisaly[j]
    j=j+1 }
    else if (s19$Away[i] == "Al-Faisaly") {
      s19$PosA[i] <- Faisaly[j]
      j=j+1}
  i=i+1}

##10
i=1
j=1
while (i<=165){
  if(s19$Home[i] == "Damac") {
    s19$PosH[i] <- Damac[j]
    j=j+1 }
    else if (s19$Away[i] == "Damac") {
      s19$PosA[i] <- Damac[j]
      j=j+1}
  i=i+1}

##11
i=1
j=1
while (i<=165){
  if(s19$Home[i] == "Al-Fayha") {
    s19$PosH[i] <- Fayha[j]
    j=j+1 }
    else if (s19$Away[i] == "Al-Fayha") {
      s19$PosA[i] <- Fayha[j]
      j=j+1}
  i=i+1}


##12
i=1
j=1
while (i<=165){
  if(s19$Home[i] == "Al-Ettifaq") {
    s19$PosH[i] <- Ettifaq[j]
    j=j+1 }
    else if (s19$Away[i] == "Al-Ettifaq") {
      s19$PosA[i] <- Ettifaq[j]
      j=j+1}
  i=i+1}

##13
i=1
j=1
while (i<=165){
  if(s19$Home[i] == "Al-Fateh") {
    s19$PosH[i] <- Fateh[j]
    j=j+1 }
    else if (s19$Away[i] == "Al-Fateh") {
      s19$PosA[i] <- Fateh[j]
      j=j+1}
  i=i+1}
##14
i=1
j=1
while (i<=165){
  if(s19$Home[i] == "Al-Shabab") {
    s19$PosH[i] <- Shabab[j]
    j=j+1 }
    else if (s19$Away[i] == "Al-Shabab") {
      s19$PosA[i] <- Shabab[j]
      j=j+1}
  i=i+1}

##15
i=1
j=1
while (i<=165){
  if(s19$Home[i] == "Al-Hazem") {
    s19$PosH[i] <- Hazem[j]
    j=j+1 }
    else if (s19$Away[i] == "Al-Hazem") {
      s19$PosA[i] <- Hazem[j]
      j=j+1}
  i=i+1}


##16
i=1
j=1
while (i<=165){
  if(s19$Home[i] == "Al-Wehda") {
    s19$PosH[i] <- Wehda[j]
    j=j+1 }
    else if (s19$Away[i] == "Al-Wehda") {
      s19$PosA[i] <- Wehda[j]
      j=j+1}
  i=i+1}



```
#Merge all the seasons
Let's now merge them
```{r}
try <- bind_rows(s10, s11, s12, s13, s14, s15, s16, s17,s18, s19)
SPL_Features <- try
remove(try)
```
Save workspace CapstoneV3 and the file

```{r}
write_csv(SPL_Features, "SPL_V1.csv")
```



